Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
minor corrections

There has been plenty of previous work that aims at \emph{verifying} a given
controller designed by the engineer.  Recent work can show the stability
digital controllers with considerations to implementation aspects, i.e.,
fixed-point arithmetic and the word length used~\cite{Bessa16}.  This work
exploits advances in bit-accurate verification of C programs to obtain a
verifier for software-implemented digital control.

@@

For this purpose, the design procedure is based on a discretised model for a
continuous plant.  Considering only transfer function models, we are
interested in a $z$-domain transfer function that considers all the aspects
about the continuous plant ($G(s)$) and the sampling and hold process.

>>>>

There has been plenty of previous work that aims at \emph{verifying} a given
controller designed by the engineer.  Recent work can show the of stability
digital controllers with considerations to implementation aspects, i.e.,
fixed-point arithmetic and the word length used~\cite{Bessa16}.  This work
exploits advances in bit-accurate verification of C programs to obtain a
verifier for software-implemented digital control.

@@

For this purpose, the design procedure is based on a discretised model for a
continuous plant.  Considering only transfer function models, we are
interested in a $z$-domain transfer function that considers all the aspects
about the continuous plant (with a Laplace domain transfer function $G(s)$) and the sampling and hold process.
